% \documentclass{article}
\documentclass[margin,line]{resume}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage[hidelinks,bookmarks=true]{hyperref}

\hypersetup{
	colorlinks=true,
	urlcolor=black,
	pdfstartview=FitH,
	pdftitle={Matteo Riondato - Curriculum Vitae},
	pdfauthor={Matteo Riondato}}

% \documentclass[margin,line]{res}
% \usepackage{multibib}
% \usepackage[top=4.5pc, bottom=5pc, inner=4.5pc, outer=4.5pc, columnsep=2pc, foot=.25in]{geometry}
%\usepackage{times}
% \usepackage{MinionPro}

% \newcites{refpaper}{Conference Papers}

%\topmargin -0.4in
\oddsidemargin -.4in
\evensidemargin -.4in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\pagestyle{fancyplain}
 
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\lhead{\fancyplain{}{}
\rfoot{\fancyplain{\thepage}{\thepage\ of 4}}

\setlength{\parskip}{4pt}
%\setlength{\parsep}{0pt}
%\setlength{\headsep}{0pt}
%\setlength{\topskip}{0pt}
%\setlength{\topmargin}{0pt}
%\setlength{\topsep}{0pt}
%\setlength{\partopsep}{0pt}

%%%
% Controls whether this is the version for the web (\webversiontrue) or not (\webversionfalse)
%%%
\newif\ifwebversion
\webversionfalse

% \newenvironment{list1}{
%   \begin{list}{\ding{113}}{%
%       \setlength{\itemsep}{0in}
%       \setlength{\parsep}{0in} \setlength{\parskip}{0in}
%       \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
%       \setlength{\leftmargin}{0.17in}}}{\end{list}}
% \newenvironment{list2}{
%   \begin{list}{$\bullet$}{%
%       \setlength{\itemsep}{0in}
%       \setlength{\parsep}{0in} \setlength{\parskip}{0in}
%       \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
%       \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcommand\T{\rule{0pt}{2.6ex}}
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}}

\begin{document}

\name{Matteo Riondato \vspace*{.1in}}
\begin{resume}

  \section{\sc Contacts}
\vspace{.05in}

%\ifwebversion
	\begin{tabular}{@{}p{2.8in}p{3.2in}}
	Stanford University & {\it Voice:} +1-401-654-3216 \\ 
	353 Serra Mall & {\it E-mail:}  rionda@cs.stanford.edu  \\
	Stanford, CA 94306, USA &  {\it WWW:} \url{http://cs.brown.edu/~matteo}  \\
	\end{tabular}

%\section{\sc Career Goal}
%{Becoming a successful scholar at a leading research institution or lab.}

\section{\sc Research Interests}

{Data analytics, pattern mining, graph mining, randomized algorithms, social
network analysis, algorithms for distributed/parallel architectures for big
data, privacy issues in data analysis, statistical learning theory.}

\section{\sc Current position}
{\bf Stanford University}, Stanford, California, USA\\
\vspace*{-.18in}
\begin{list1}
\item[] Postdoctoral Researcher, since August 2014
\begin{list2}
\item Supervisor: Prof.~Chris R\'e
\end{list2}
\end{list1}

\section{\sc Education}
{\bf Brown University}, Providence, Rhode Island, USA\\
\vspace*{-.18in}
\begin{list1}
\item[] Ph.D., Computer Science, May 2014
\begin{list2}
%\vspace*{.05in}
\item Dissertation: {\em Sampling-based randomized algorithms for Big Data analytics}
\item Advisor: Prof.~Eli Upfal 
\item Best student poster award at SIAM Int.~Conf. on Data Mining (SDM'14), April 2014.
\end{list2}
\item[] M.Sc., Computer Science, May 2010
\end{list1}

{\bf Universit\`a di Padova}, Padua, Italy\\
\vspace*{-.18in}
\begin{list1}
\item[] Laurea Magistrale (M.Sc.) 110/110 \textit{cum laude}, Computer Engineering, July 2009
\begin{list2}
\item Master Thesis: {\em Top-k frequent itemsets mining through sampling}
\item Advisors: Prof.~Andrea Pietracaprina, Prof.~Eli Upfal, Fabio Vandin
\end{list2}
\item[] Laurea (B.Sc.), Information Engineering, July 2007
\begin{list2}
\item Final Project: {\em Algorithmical foundations of cryptography}
\item Advisor: Prof.~Andrea Pietracaprina
\end{list2}
\end{list1}
\end{resume}
  
%\section{\sc Current Research}
\section{\sc Publications}

[13] A.~Anagnastopoulos, L.~Becchetti, A.~Fazzone, I.~Mele, and M.~Riondato.
\newblock The importance of being experts: Efficient max-finding in
crowdsourcing.
\newblock To appear in {\em ACM SIGMOD Int.~Conf.~on Management of Data,
SIGMOD'15, Melbourne, Australia, May 31 -- June 4, 2015}.

[12] M.~Riondato, D.~Garc\'ia-Soriano, and F.~Bonchi.
\newblock Graph summarization with quality guarantees
\newblock {\em 14th IEEE Int.~Conf.~on Data Mining, ICDM'14, Shenzen,
China, December 14--17, 2014}.

[11] M.~Riondato.
\newblock Sampling-based data mining algorithms: Modern techniques and case
  studies.
\newblock {\em European Conf.~on Mach.~Learn.~and Knowl.~Disc.~in Databases,
ECML PKDD'14, Nancy, France, September 15--19, 2014}.

[10] M.~Riondato and F.~Vandin.
\newblock Finding the true frequent itemsets.
\newblock {\em 14th SIAM Int.~Conf.~on Data Mining,
SDM'14, Philadelphia, PA, USA, April 24--26, 2014}.

[9] M.~Riondato and E.~Upfal.
\newblock Efficient discovery of association rules and frequent itemsets through
sampling with tight performance guarantees.
\newblock {\em ACM Trans.~on Knowl.~Disc.~from Data}, 8(4):20, 2014.

[8] M.~Riondato and E.~M.~Kornaropoulos.
\newblock Fast approximation of betweenness centrality through sampling.
\newblock {\em 7th ACM Int.~Conf.~on Web Search and Data Mining,
WSDM'14, New York, NY, USA, February 24--28, 2014}.

%\bibitem{RiondatoDFU12}
[7] M.~Riondato, J.~A.~DeBrabant, R.~Fonseca, and E.~Upfal.
\newblock {PARMA}: A parallel randomized algorithm for association rules mining
  in {MapReduce}.
\newblock {\em 21st ACM Int.~Conf.~on Inform.~and Knowl.~Manag., CIKM'12, Maui, HI,
  USA, October 29 -- November 02, 2012}.

%\bibitem{RiondatoU12}
[6] M.~Riondato and E.~Upfal.
\newblock Efficient discovery of association rules and frequent itemsets
  through sampling with tight performance guarantees.
\newblock {\em European Conf.~on Mach.~Learn.~and Knowl.~Disc.~in Databases,
ECML PKDD'12, Bristol, UK, September 24--28, 2012}.

%\bibitem{PietracaprinaPRSU12}
[5] A.~Pietracaprina, G.~Pucci, M.~Riondato, F.~Silvestri, and E.~Upfal.
\newblock Space-round tradeoffs for {MapReduce} computationseduce computations.
\newblock {\em ACM Int.~Conf.~on Supercomputing, ICS'12, Venice,
  Italy, June 25--29, 2012}.

%\bibitem{AkdereCRUZ12}
[4] M.~Akdere, U.~\c{C}etintemel, M.~Riondato, E.~Upfal, and S.~B.~Zdonik.
\newblock Learning-based query performance modeling and prediction.
\newblock {\em 28th IEEE Int.~Conf.~on Data Engin., ICDE'12, April 1--5, 2012, Washington, DC, USA}.

%\bibitem{RiondatoACZU11}
[3] M.~Riondato, M.~Akdere, U.~\c{C}etintemel, S.~B.~Zdonik, and E.~Upfal.
\newblock The {VC}-dimension of {SQL} queries and selectivity estimation
  through sampling.
\newblock {\em European Conf.~on Mach.~Learn.~and Knowl.~Disc.~in Databases,
ECML PKDD'11, Athens, Greece, September 5--9, 2011}.

%\pagebreak

%\bibitem{AkdereCRUZ11}
[2] M.~Akdere, U.~\c{C}etintemel, M.~Riondato, E.~Upfal, and S.~B.~Zdonik.
\newblock The case for predictive database systems: Opportunities and
  challenges.
\newblock {\em 5th Biennial Conf.~on Innovative Data Sys.~Research, CIDR'11,
Asilomar, CA, USA, January 9--12, 2011}.

%\bibitem{PietracaprinaRUV10}
[1] A.~Pietracaprina, M.~Riondato, E.~Upfal, and F.~Vandin.
\newblock Mining top-k frequent itemsets through progressive sampling.
\newblock {\em Data Mining and Knowl.~Disc.}, 21(2):310--326 (special issue for
ECML PKDD'10), 2010.

%\subsection{\sc \small Under Submission}


\section{\sc Awards}

SIAM Best Student Poster Award at SIAM SDM'14 \hfill {\bf April 2014}

SIAM Student Travel Grant to SIAM SDM'14 \hfill {\bf April 2014}

Brown University Dissertation Fellowship \hfill {\bf Fall 2013}

Yahoo!~Research Summer Internship \hfill {\bf Summer 2013}

Research Fellowship from MIUR of Italy under Project AlgoDeep prot.~2008TFBWL4
\hfill {\bf Summer 2011}

Brown University Graduate Fellowship \hfill {\bf Academic Year 2009--10}

\section{\sc Invited Talks}

Efficient Frequent Itemsets mining through sampling
\newblock{\em Database Research Group Seminar, University of Waterloo}, 5/7/2014.

Efficient Frequent Itemsets mining through sampling
\newblock{\em Database Group Seminar, MIT CSAIL},
04/10/2014.

Taming the challenges of Big Data with statistical data analytics.
\newblock{\em Department of Computer Science, Boston College}, 02/07/2014.

Fast betweenness estimation through sampling.
\newblock{\em Data Management Group Seminar, Boston University}, 10/17/2013.

Fast betweenness estimation through sampling.
\newblock{\em Lab Research Seminar, Yahoo!~Labs Barcelona}, 6/13/2013.

Fast betweenness estimation through sampling.
\newblock{\em Advanced Computing Group Talk, Department of Information
Engineering, University of Padua, Italy}, 5/30/2013.

Statistical learning theory meets knowledge discovery: Randomized algorithms for
Big Data analytics.
\newblock{\em Brown CS Industrial Partners Program Symposium}, 4/25/2013.

Approximate aggregate database queries through sampling.
\newblock{\em Invited Lecture for CSCI-2950-T, Brown University}, 10/25/2011.

Graphs algorithms in MapReduce: Design choices and optimizations.
\newblock{\em Invited Lecture for CSCI-2950-U, Brown University}, 9/27/2011.

Statistical learning theory meets databases.
\newblock{\em Advanced Computing Group Talk, Department of Information
Engineering, University of Padua, Italy}, 06/24/2011.

Top-k frequent itemsets mining through sampling.
\newblock{\em Advanced Computing Group Talk, Department of Information
Engineering, University of Padua, Italy}, 9/16/2010.


\section{\sc Additional Research Experience}
{\bf Yahoo!~Labs}, Barcelona, Spain \\
{\em Summer Intern Research Scientist in the Web Mining Group} \hfill {\bf June -- August 2013}

\begin{list2}
\vspace*{.05in}
\item Worked with Dr.~Francesco Bonchi and others on algorithms for graph
  summarization and for frequent itemsets mining from data streams in a
  distributed setting.
\end{list2}

{\bf Summer School on Massive Data Mining}, Copenhagen, Denmark \\
{\em Student} \hfill {\bf August 8 -- 10, 2012}

\begin{list2}
  \vspace*{.05in}
\item Attended the Summer School on Massive Data Mining organized by
  Prof.~R.~Pagh at IT University of Copenhagen.
\end{list2}

\pagebreak
{\bf Sapienza Universit\`a di Roma}, Rome, Italy\\
{\em Visiting Ph.D.~Student} \hfill {\bf June -- July 2012}

\begin{list2}
\vspace*{.05in}
\item Worked with Prof.~S.~Leonardi, A.~Anagnostopoulos, and L.~Becchetti on
  algorithms for a model of crowdsourcing computation, and on algorithms for
  MapReduce.
\end{list2}

{\bf Universit\`a di Padova}, Padua, Italy\\
{\em Research Fellow} \hfill {\bf May -- July 2011}

\begin{list2}
\vspace*{.05in}
\item Worked with Prof.~A.~Pietracaprina, G.~Pucci, and F.~Silvestri on ``The MapReduce Paradigm:
computational model and algorithms''. Funded by MIUR of Italy under Project AlgoDEEP prot.~2008TFBWL4.
\end{list2}

{\bf Chalmers University of Technology}, Gothemburg, Sweden\\
{\em Visiting Ph.D.~Student} \hfill {\bf August 2010}

\begin{list2}
\vspace*{.05in}
\item Worked with Prof.~Devdatt Dubhashi and helped organize a seminar on Probability and Computing.
\end{list2}

{\bf Brown University}, Providence, RI, USA\\
{\em Visiting Grad Student} \hfill {\bf October 2008 -- June 2009}

\begin{list2}
\vspace*{.05in}
\item Worked with Prof.~Eli Upfal on master thesis \textit{Top-K Frequent
  Itemsets Mining through Sampling}.
\end{list2}

\section{\sc Teaching and Advising Training and Experience}
{\bf The Harriet W. Sheridan Center for Teaching and Learning (Brown
University)}, Providence, RI, USA
\begin{list2}
\vspace*{.05in}
\item Teaching Certificate I: Reflective Learning, AY 2013--14
\end{list2}

{\bf Brown University}, Providence, Rhode Island, USA

\begin{list2}
\vspace*{.05in}
\item Mentor, New Scientist Program Graduate-Undergraduate Mentoring Initiative, Spring 2014
\item Teaching Assistant, Probability and Computing, Spring 2012, Spring 2013, Spring 2014
\item Teaching Assistant, Probabilistic Methods in Computer Science, Fall 2010 
\end{list2}

\section{\sc Service}
{\bf PC member for CIKM'14 (Knowledge Management track) }

{\bf Reviewer for IEEE TKDE}

{\bf Reviewer for the following conferences}
\begin{list2}
\vspace*{.05in}
\item RANDOM'11, ICS'12, IPDPS'12, WSDM'13, MFCS'13, BigData'13, WSDM'14,
  DISC'14.
\end{list2}

{\bf Brown University Graduate Student Council}\\
{\em President} \hfill {\bf April 2011 -- December 2012}

\begin{list2}
\vspace*{.05in}
\item Represented the interests of the entire graduate student community
  (approx.~2000 students) with the university administration and the broader
  community at all levels. Previously held positions include Vice-President of
  Administration (Jan. -- April 2011) and representative for the Computer Science
  Department (Sept.~2009 -- April 2011, Jan 2013 -- \emph{ongoing}).
\end{list2}

{\bf Brown University Graduate Council}\\
{\em Student Representative} \hfill {\bf September 2011 -- May 2013}

\begin{list2}
\vspace*{.05in}
\item Represented the graduate student community in the highest
  body governing graduate education.
\end{list2}

{\bf Brown University Strategic Planning Committee on Doctoral Education}\\
{\em Student Representative} \hfill {\bf September 2012 -- May 2013}

\begin{list2}
\vspace*{.05in}
\item Represented the graduate student community to develop
  the presidential strategic plan for the next decade.
\end{list2}

{\bf Brown Computer Science Theory Lunch}\\ 
{\em Organizer} \hfill {\bf January -- December 2010 }

\begin{list2}
\vspace*{.05in}
\item Responsible for organizing the weekly meeting of the Theory Group. 
  %Duties
  %including finding speakers, both external and internal to the department, and
  %volunteers for bringing lunch. 
\end{list2}

\section{\sc Membership}
{\bf Association for Computing Machinery (ACM)}
\begin{list2}
\vspace*{.05in}
\item Student member and member of Special Interest Group on Knowledge Discovery
  from Data (SIGKDD).
\end{list2}
{\bf Institute of Electrical and Electronic Engineers (IEEE)}
\begin{list2}
\vspace*{.05in}
\item Student member and member of IEEE Computer Society.
\end{list2}
{\bf Society for Industrial and Applied Mathematics (SIAM)}
\begin{list2}
\vspace*{.05in}
\item Student member and member of SIAM Activity Group on Data Mining and Analytics
  (SIAG/DMA).
\end{list2}

%\pagebreak
\pagebreak
\section{\sc Software}

{\bf CentrSampl}
\begin{list2}
  \vspace*{.05in}
\item Algorithm to estimate node betweenness centrality in large graphs. Based
  on [8]. \\\url{http://cs.brown.edu/~matteo/centrsampl.tar.bz2} .
\end{list2}

{\bf PARMA} 
\begin{list2}
  \vspace*{.05in}
\item Frequent itemsets and association rules mining algorithm for Hadoop MapReduce.
  Based on [7]. \\\url{http://cs.brown.edu/~matteo/parma.tar.bz2} .
\end{list2}

{\bf FreeSBIE }\\
{\em Developer, Release Engineer for the 2.x series} \hfill{\bf April 2004 --
July 2009}

\begin{list2}
\vspace*{.05in}
\item Developed FreeSBIE, a Live-CD distribution of FreeBSD bootable from CD-ROM.
Release Engineer for FreeSBIE 2.X.~series, responsible for all aspects of
the release. \url{http://www.FreeSBIE.org} .
\end{list2}

{\bf The FreeBSD Project}\\
{\em \textrm{src} Committer} \hfill {\bf January 2006 -- June 2013}

\begin{list2}
\vspace*{.05in}
\item Contributed to the development of the FreeBSD UNIX operating system.
  Granted write access to the main source repository. Worked on the
  \texttt{jail} security feature and on handling and solving bug reports of
  various nature. Author of the \emph{Jail} chapter in the FreeBSD Handbook.
  \url{http://www.FreeBSD.org} .
\end{list2}

%\pagebreak
\section {\sc References}
\begin{table}[h!]
  \centering
  \begin{tabular}{lll}
    Prof.~Eli Upfal & Prof.~U\u{g}ur \c{C}etintemel & Dr.~Francesco Bonchi \\
    Dept.~of Computer Science & Dept.~of Computer Science & Yahoo!~Labs Barcelona
    \\
    Brown University & Brown University & Yahoo! \\
    \url{eli@cs.brown.edu} & \url{ugur@cs.brown.edu} &
    \url{bonchi@yahoo-inc.com} \\
  \end{tabular}
\end{table}

\iffalse
\section {\sc Technical Skills}
{\bf Programming Languages}
\begin{list2}
\vspace*{.05in}
\item Fluent in the following languages: C/C++, Python, Java, and bash.
\end{list2}

{\bf Operating Systems}
\begin{list2}
  \vspace*{.05in}
\item Expert user and administrator of FreeBSD systems and various flavours of GNU/Linux
  distributions.
\end{list2}

\section {\sc Citizenship}

Italian

\section{\sc Updated}
\today
\fi

\section{\sc Up-to-date version} Available from~\url{http://cs.brown.edu/~matteo/matteo\_riondato\_cv.pdf}


\end{document}

