\documentclass{article}

\title{List of Publications}
\author{Matteo Riondato}
\date{ }
\begin{document}
\maketitle

\section*{Journals}

\noindent M. Riondato and E.~M.~Kornaropoulos.
\newblock Fast approximation of betweenness centrality through sampling.
\newblock To appear in {\em Data Mining and Knowl.~Disc.}, 2015.

$ $

\noindent M.~Riondato and E.~Upfal.
\newblock Efficient discovery of association rules and frequent itemsets through
sampling with tight performance guarantees.
\newblock {\em ACM Trans.~on Knowl.~Disc.~from Data}, 8(4):20, 2014.

$ $

\noindent A.~Pietracaprina, M.~Riondato, E.~Upfal, and F.~Vandin.
\newblock Mining top-k frequent itemsets through progressive sampling.
\newblock {\em Data Mining and Knowl.~Disc.}, 21(2):310--326 (special issue for
ECML PKDD'10), 2010.

\section*{International Peer-reviewed Conferences}

\noindent A.~Anagnastopoulos, L.~Becchetti, A.~Fazzone, I.~Mele, and M.~Riondato.
\newblock The importance of being experts: Efficient max-finding in
crowdsourcing.
\newblock To appear in {\em ACM SIGMOD Int.~Conf.~on Management of Data,
SIGMOD'15, Melbourne, Australia, May 31 -- June 4, 2015}.

$ $

\noindent M.~Riondato, D.~Garc\'ia-Soriano, and F.~Bonchi.
\newblock Graph summarization with quality guarantees
\newblock {\em 14th IEEE Int.~Conf.~on Data Mining, ICDM'14, Shenzen,
China, December 14--17, 2014}.

$ $

\noindent M.~Riondato.
\newblock Sampling-based data mining algorithms: Modern techniques and case
  studies.
\newblock {\em European Conf.~on Mach.~Learn.~and Knowl.~Disc.~in Databases,
ECML PKDD'14, Nancy, France, September 15--19, 2014}.

$ $

\noindent M.~Riondato and F.~Vandin.
\newblock Finding the true frequent itemsets.
\newblock {\em 14th SIAM Int.~Conf.~on Data Mining,
SDM'14, Philadelphia, PA, USA, April 24--26, 2014}.

$ $

\noindent M.~Riondato and E.~M.~Kornaropoulos.
\newblock Fast approximation of betweenness centrality through sampling.
\newblock {\em 7th ACM Int.~Conf.~on Web Search and Data Mining,
WSDM'14, New York, NY, USA, February 24--28, 2014}.

$ $

%\bibitem{RiondatoDFU12}
\noindent M.~Riondato, J.~A.~DeBrabant, R.~Fonseca, and E.~Upfal.
\newblock {PARMA}: A parallel randomized algorithm for association rules mining
  in {MapReduce}.
\newblock {\em 21st ACM Int.~Conf.~on Inform.~and Knowl.~Manag., CIKM'12, Maui, HI,
  USA, October 29 -- November 02, 2012}.

$ $

%\bibitem{RiondatoU12}
\noindent M.~Riondato and E.~Upfal.
\newblock Efficient discovery of association rules and frequent itemsets
  through sampling with tight performance guarantees.
\newblock {\em European Conf.~on Mach.~Learn.~and Knowl.~Disc.~in Databases,
ECML PKDD'12, Bristol, UK, September 24--28, 2012}.

$ $

%\bibitem{PietracaprinaPRSU12}
\noindent A.~Pietracaprina, G.~Pucci, M.~Riondato, F.~Silvestri, and E.~Upfal.
\newblock Space-round tradeoffs for {MapReduce} computations.
\newblock {\em ACM Int.~Conf.~on Supercomputing, ICS'12, Venice,
  Italy, June 25--29, 2012}.

$ $

%\bibitem{AkdereCRUZ12}
\noindent M.~Akdere, U.~\c{C}etintemel, M.~Riondato, E.~Upfal, and S.~B.~Zdonik.
\newblock Learning-based query performance modeling and prediction.
\newblock {\em 28th IEEE Int.~Conf.~on Data Engin., ICDE'12, April 1--5, 2012, Washington, DC, USA}.

$ $

%\bibitem{RiondatoACZU11}
\noindent M.~Riondato, M.~Akdere, U.~\c{C}etintemel, S.~B.~Zdonik, and E.~Upfal.
\newblock The {VC}-dimension of {SQL} queries and selectivity estimation
  through sampling.
\newblock {\em European Conf.~on Mach.~Learn.~and Knowl.~Disc.~in Databases,
ECML PKDD'11, Athens, Greece, September 5--9, 2011}.

$ $

%\bibitem{AkdereCRUZ11}
\noindent M.~Akdere, U.~\c{C}etintemel, M.~Riondato, E.~Upfal, and S.~B.~Zdonik.
\newblock The case for predictive database systems: Opportunities and
  challenges.
\newblock {\em 5th Biennial Conf.~on Innovative Data Sys.~Research, CIDR'11,
Asilomar, CA, USA, January 9--12, 2011}.

%\nocite{*}
%\bibliography{riondapubs}{}
%\bibliographystyle{abbrv}
\end{document}
